ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-25 pyked.tex
Use microtype
Add more about PyKED arch

\usepackage{todonotes}
\newcommand\ck{ChemKED}
\newcommand\pk{PyKED}
\usepackage[inline]{enumitem}
\setlist{noitemsep}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

The basic user interface to the \ck{} file in \pk{} is through the
\python|ChemKED| class. The \python|ChemKED| class constructor takes the file
name of a \ck{} file or a Python dictionary containing the contents of a \ck{}
file as its argument. When the file or dictionary is loaded, it is validated to
have the correct format by Cerberus \autocite{cerberus}. The fields of the \ck{}
file are stored as instance attributes of the \python|ChemKED| class.

>>>>

\usepackage{todonotes}

\newcommand\ck{ChemKED}
\newcommand\pk{PyKED}

\usepackage[inline]{enumitem}
\setlist{noitemsep}

\usepackage{microtype}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

The basic user interface to the \ck{} file in \pk{} is through the
\python|ChemKED| class. The \python|ChemKED| class constructor takes the file
name of a \ck{} file or a Python dictionary containing the contents of a \ck{}
file as its argument. When the file or dictionary is loaded, it is validated to
have the correct format by Cerberus \autocite{cerberus}.

The fields of the \ck{} file are stored as instance attributes of the
\python|ChemKED| class. The following attributes are available with the
appropriate data:
%
\begin{itemize}
    \item \python|chemked_version|, \python|file_version|, \python|file_author|,
    \python|experiment_type|: Stores the values from the \ck{} file
    \item \python|reference|: Instance of a \python|namedtuple| containing all
    the information from the literature reference associated with the data
    \item \python|apparatus|: Instance of a \python|namedtuple| containing all
    the information about the apparatus used to perform the experiment
    \item \python|datapoints|: A Python list of \python|DataPoint| instances
\end{itemize}

The \python|DataPoint| class stores the information associated with a single
data point in the \ck{} file. Similar to the \python|ChemKED| class, the
information from the \ck{} file are stored as attributes of class instances,
including
%
\begin{itemize}
    \item \python|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only, no validation is done of the value
    \item \python|ignition_delay|, \python|temperature|, \python|pressure|,
    \python|pressure_rise|: The value of these data are stored as instances of
    the \python|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \python|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yaml|mole-percent|,
    \yaml|mole-fraction|, or \yaml|mass-fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yaml|mole-percent|.
    \item \python|composition_type|: A string indicating the type of composition
    information for the data point---one of \python|'mole-percent'|,
    \python|'mole-fraction'|, or \python|'mass-fraction'|
    \item \python|volume_history|: If the \yaml|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \python|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}.
\end{itemize}

The \python|DataPoint| class has two instance methods defined, called
\python|get_cantera_mole_fraction| and \python|get_cantera_mass_fraction|. With
these methods, the composition of the reactant mixture can be output to a format
that can be used to set the composition of a Cantera \python|Solution|. Note
that the \python|composition| specification is not required to contain the
molecular weights of the components, so calling
\python|get_cantera_mass_fraction| when \yaml|mole-percent| or
\yaml|mole-fraction| has been used in the \ck{} file will raise a
\python|ValueError| (and vice versa for \python|get_cantera_mole_fraction|).
